Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-05 astronum_2017/astronum-amrex.tex
more reproducibile
update fig
more plots

\newcommand{\maestro}{{\sffamily Maestro}}
\newcommand{\castro}{{\sffamily Castro}}
\newcommand{\starkiller}{{\sffamily StarKiller}}
\newcommand{\nyx}{{\sffamily Nyx}}
\newcommand{\amrex}{{\sffamily AMReX}}

@@

All of our simulation codes are open source and follow a fully open
development model---the development git repos are hosted on
github\footnote{\url{https://github.com/AMReX-Astro/}}, available for
anyone to see and contribute to using issues and pull-requests.
{\em All source files, model files, input parameters, etc.\ for any
published science results are also available in the code repos.}  When
feasible, the git hashes for the published results are included in paper
acknowledgements.

regression testing

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{titan_xrb_scaling}
\caption{\label{fig:maestro_scaling} blah}
\end{figure}

>>>>

\newcommand{\maestro}{{\sffamily Maestro}}
\newcommand{\castro}{{\sffamily Castro}}
\newcommand{\starkiller}{{\sffamily StarKiller}}
\newcommand{\starlord}{{\sffamily StarLord}}
\newcommand{\nyx}{{\sffamily Nyx}}
\newcommand{\amrex}{{\sffamily AMReX}}

@@

All of our simulation codes are open source and follow a fully open
development model---the development git repos are hosted on
github\footnote{\url{https://github.com/AMReX-Astro/}}, available for
anyone to see and contribute to using issues and pull-requests.
New changes are put into the {\tt development} branch in each repo.
Nightly regression testing is used to ensure that no new bugs were
introduced.  Once a month, {\tt development} is merged into {\tt
  master}.
{\em All source files, model files, input parameters, etc.\ for any
published science results are also available in the code repos.}  When
feasible, the git hashes for the published results are included in paper
acknowledgements.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{titan_edison_maestro_scaling}
\includegraphics[width=0.48\linewidth]{summitdev_scaling}
\caption{\label{fig:scaling} (left) \maestro\ strong scaling on NERSC edison
and OCLF titan for a 3-d XRB problem.  Two different problem sizes are show.
(right) \starlord\ scaling across nodes on the OLCF summitdev platform, using
up to 4 GPUs per node.}
\end{figure}
